Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-06-17 Manuscript.Rmd
new formatting for journal submission

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort
  and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1,2^, Gary A. Kane^1,2^, & Joseph T. McGuire^1,2^"
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
- \usepackage{indentfirst}
- \usepackage{fixltx2e}
output:
  pdf_document:
    highlight: haddock
    keep_tex: no
    fig_caption: yes
csl: apa.csl
indent: true
bibliography: bibliography.bib
geometry: margin=1in
---

@@

Corresponding authors: Claudio Toro-Serey (ctoroserey@mclean.harvard.edu) & Joseph T. McGuire (jtmcg@bu.edu)

>>>>

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort
  and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1,2^, Gary A. Kane^1,2^, & Joseph T. McGuire^1,2^"
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
- \usepackage{indentfirst}
- \usepackage{fixltx2e}
- \pagestyle{myheadings}
output:
  pdf_document:
    highlight: haddock
    keep_tex: no
    fig_caption: yes
csl: apa.csl
indent: true
bibliography: bibliography.bib
geometry: margin=1in
---

@@

**Corresponding authors**:

\begin{itemize}
  \item[] Claudio Toro-Serey
  \item[] McLean Hospital
  \item[] 115 Mill St., MRC 3, Belmont, MA 02478
  \item[] (859) 619-7217
  \item[] ctoroserey@mclean.harvard.edu
\end{itemize}

\bigskip
\bigskip

\begin{itemize}
  \item[] Joseph T. McGuire
  \item[] Boston University
  \item[] 677 Beacon St., Rm 212, Boston, MA 02215
  \item[] (617) 353-7670
  \item[] jtmcg@bu.edu
\end{itemize}
